Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-03-31 paper/paper.tex
20200331 13:33
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

\begin{abstract}
\textcolor{red}{The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. $\cdots \cdots$}
\end{abstract}

@@

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Kitaev-Heisenberg (KH) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the KH model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

@@

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases. In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases. $S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

@@

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For the classical FM order, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction. Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.

@@

In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian. We consider a $4 \times 6$ cluster with PBC that has been used previously to study the KH model on triangular lattice \cite{KaiLi2015}. The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a). The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$. The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.

\subsection{\label{subsec:HKLimit}Phases in the HK limit ($\Gamma=0$)}
For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the HK ($\Gamma=0$) model, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases can be identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$
\begin{align*}
    & \bm{S}_{0}^{'} = \bm{S}_{0}& \quad \text{for sublattice 0} \\
    & \bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1} \\
    & \bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2} \\
    & \bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}
\end{align*}
The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).

Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}. To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(c). It is clear from Fig.~\ref{fig:StructureFactors}(c) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.

To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(c) and Fig.~\ref{fig:Proabilities}(f). The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(f) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it a signature of large quantum flucations in the ground state. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively. (c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
\end{figure}

>>>>

\begin{abstract}
The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. The quantum phase diagram is quite similar to the classical case except for a small area of possible QSL near the $\Gamma=1$ point. The continuum in the spin excitation spectrum and no spectrum intensity at zero energy indicates that the ground state of the model in this area is gapped QSL. As for the exotic phase near the antiferromagetic Kitaev point, our exact diagnoalization results provide evidence that it is stripe phase and the ordered moment along the cubic axes direction. In adition to the identification of these novel phases, we made a detailed distinction between these FM and stripe phases which occupy the majority area of the global phase diagram.
\end{abstract}

@@

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

@@

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a detailed discussion of its phases.

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases. $S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

@@

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For classical FM states, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction. Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.

@@

In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian. We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}. The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a). The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$. The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.

\subsection{\label{subsec:HKLimit}Phases in the HK limit ($\Gamma=0$)}
For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the HK ($\Gamma=0$) model, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases can be identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$
\begin{align*}
    & \bm{S}_{0}^{'} = \bm{S}_{0}& \quad \text{for sublattice 0} \\
    & \bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1} \\
    & \bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2} \\
    & \bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}
\end{align*}
The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (Dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and Fig.~\ref{fig:PhaseDiagram}(f)).

Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}. To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(a). It is clear from Fig.~\ref{fig:StructureFactors}(a) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.

To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(a) and Fig.~\ref{fig:Proabilities}(b). The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
\end{figure}

\subsection{\label{subsec:GammaEffects}Effects of the $\Gamma$ term}
When the off-diagonal $\Gamma$ term is included, the FST is no longer valid. To study the nature of these remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(b) and (c), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Bases on this observation, we propose the areas containing the $\Gamma=\pm 1$ points in the global phase diagram to be FM ordered phases (i.e., FM-A, FM-C). To further confirm our hypothesis, we construct cluster spin-coherent states with all the spins are polarized along the $(\theta, \phi)$ direction. By inspecting the probability map $P(\theta, \phi)$, we can measure the presence of the cluster spin-coherent states in the exact cluster GS. The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(c) and \ref{fig:Proabilities}(d). The large overlap between the exact cluster GS and FM ordered cluster spin-coherent state provides solid evidence that the corresponding areas are FM phases. For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)). The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states. Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS. In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction. When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.
